Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-11-30 doc/om-paper/paper.tex
Answer questions at end of scalability subsecion

\lee{let's also check out scalability when we ``turn off'' faults. Also, how hard is it to turn them off or change the fault model? E.g., how many lines of spec need to be changed? Compare to rushby's?}
\lee{what are the machine specs for running the benchmark?}

>>>>

The benchmarks were performed on a server with Intel Xeon E312xx (Sandy
Bridge) CPUs (mid 2011).

For comparison, when the fault model is ``turned off'' by defining the fault
type to contain a single 'nonfaulty' value and removing fault specific lemmas,
model-checking scales further. For example when there are 3 relays and 3
receivers the time is 25s (compared to 40s above), and when where are 5 relays
and 5 receivers the time is 315s (compared to timeout above). See Figure
\ref{fig:effort} for more comparisons.
